\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{titlesec}
\usepackage{xcolor}

\geometry{left=0.6in, right=0.6in, top=0.5in, bottom=0.5in}

\definecolor{linkblue}{HTML}{0066CC}
\definecolor{rulecolor}{HTML}{2C3E50}
\hypersetup{colorlinks=true, linkcolor=linkblue, urlcolor=linkblue}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\color{rulecolor}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

\setlist{noitemsep, topsep=2pt, leftmargin=16pt}
\pagestyle{empty}

\begin{document}

% ─── HEADER ───
\begin{center}
{\LARGE \textbf{M KARTHIKEYAN}}\\[4pt]
{\normalsize AI Engineer \(\mid\) Machine Learning Specialist \(\mid\) OT Security Analytics}\\[6pt]
\faPhone\ +91 9380699461 \quad
\faEnvelope\ \href{mailto:karthikeyan17802@gmail.com}{karthikeyan17802@gmail.com} \quad
\faLinkedin\ \href{https://www.linkedin.com/in/karthikeyan-m-10a35a242/}{LinkedIn}\\[4pt]
\faGlobe\ \textbf{Portfolio:} \href{https://karthikeyan1708.github.io}{\textcolor{linkblue}{karthikeyan1708.github.io}} --- \textit{Interactive portfolio with projects, engagements \& experience}
\end{center}

% ─── OBJECTIVE ───
\section{Objective}
AI Engineer with \textbf{1.8+ years} at PricewaterhouseCoopers, specializing in production-grade machine learning pipelines for industrial cybersecurity. Seeking opportunities to apply expertise in anomaly detection, large-scale data engineering, and AI-powered threat analysis to build impactful, scalable solutions.

% ─── EDUCATION ───
\section{Education}
\textbf{B.Tech, Computer Science \& Engineering (Artificial Intelligence)} \hfill \textit{2020--2024}\\
\textit{School of AI \& Computing, Amrita Vishwa Vidyapeetham, Coimbatore} \hfill CGPA: 8.5 / 10\\[2pt]
\textit{Key Coursework:} Machine Learning, Deep Learning, NLP, Computer Vision, Data Structures \& Algorithms, Software Engineering

% ─── EXPERIENCE ───
\section{Experience}
\textbf{Associate -- AI \& OT Cybersecurity} \hfill \textit{Oct 2024 -- Present}\\
\textit{PricewaterhouseCoopers (PwC), Hyderabad} \hfill \textit{1.8+ years}

\vspace{4pt}
\textbf{AI-Driven Security Analytics}
\begin{itemize}
  \item Designed and deployed an \textbf{ML-based anomaly detection pipeline} processing 500K+ daily OT sensor events, achieving 85\% precision and reducing false-positive rates by 30\%.
  \item Engineered Python workflows to ingest and analyze \textbf{multi-terabyte PCAP datasets}, extracting 50+ protocol-level features for downstream classification models.
  \item Developed an \textbf{XGBoost risk-scoring engine} that ranked vulnerabilities by exploitability and asset criticality, cutting manual triage time by \textbf{40\%}.
  \item Built reusable \textbf{NLP pipelines} to parse security policy documents and identify compliance gaps against ISO 27001:2022 controls with 90\%+ extraction accuracy.
\end{itemize}

\vspace{4pt}
\textbf{Assessment Delivery}
\begin{itemize}
  \item Delivered \textbf{6 end-to-end OT security assessments} across aviation, energy, telecom, and manufacturing -- encompassing network architecture review, stakeholder workshops, and executive reporting.
  \item Executed on-site audits across \textbf{4 geographically distributed sites} under aggressive 3-week timelines, delivering maturity assessments with prioritized remediation roadmaps.
  \item Performed \textbf{firewall rule analysis and network segmentation reviews} for industrial control environments, uncovering 25+ critical misconfigurations per engagement.
  \item Conducted physical and logical security reviews of telecom infrastructure across 5 tower locations, scripting configuration compliance checks in Python.
\end{itemize}

\vspace{4pt}
\textbf{SOC Operations \& Continuous Monitoring}
\begin{itemize}
  \item Providing \textbf{24/7 shift-based SOC support} for a global industrial technology provider -- real-time threat monitoring, alert triage, and incident escalation using Microsoft Sentinel and Defender for IoT.
\end{itemize}

% ─── PROJECTS ───
\section{Projects}

\textbf{Automatic Speech Recognition \& Emotion Detection -- Tamil Language} \hfill \textit{Apr--May 2024}
\begin{itemize}
  \item Fine-tuned OpenAI's \textbf{Whisper Base} model with transfer learning on a custom Tamil-speech corpus; appended bidirectional LSTM layers for temporal emotion modeling, achieving \textbf{85\% accuracy} across 6 emotion categories.
  \item Designed a robust data pipeline handling audio augmentation (noise injection, pitch shifting, time stretching), MFCC/spectrogram extraction, and batch processing of 12+ hours of raw audio daily.
  \item Deployed inference endpoint via FastAPI with sub-200ms latency; containerized with Docker for reproducible deployment.
\end{itemize}

\vspace{4pt}
\textbf{Communicable Disease Outbreak Prediction System} \hfill \textit{Jan--Mar 2023}
\begin{itemize}
  \item Developed an ensemble of \textbf{RNN and SVR models} to forecast dengue and chikungunya outbreaks with \textbf{92\% accuracy} over a 12-month prediction horizon.
  \item Engineered 30+ features from epidemiological, meteorological, and demographic datasets totaling 2M+ records; applied PCA and recursive feature elimination for dimensionality reduction.
  \item Built interactive Plotly dashboards for public-health stakeholders, enabling drill-down analysis by region, time period, and disease type.
  \item \textbf{Published} in Springer -- \textit{Inventive Communication and Computational Technologies} (Oct 2023).
\end{itemize}

% ─── SKILLS ───
\section{Technical Skills}
\begin{itemize}
  \item \textbf{Languages:} Python (Advanced), SQL, MATLAB, Java
  \item \textbf{ML/DL Frameworks:} TensorFlow, PyTorch, Keras, Scikit-learn, XGBoost, Hugging Face, ONNX
  \item \textbf{Data \& Visualization:} NumPy, Pandas, Dask, Matplotlib, Seaborn, Plotly, Power BI
  \item \textbf{MLOps \& DevOps:} Docker, Git, CI/CD (GitHub Actions), FastAPI, REST APIs, Linux
  \item \textbf{Cloud:} AWS (S3, SageMaker, Lambda), Azure (Sentinel, Blob Storage)
  \item \textbf{Security Tools:} Wireshark, Claroty, Tenable, PCAP Analysis, OT/ICS Protocol Analysis
\end{itemize}

% ─── CERTIFICATIONS ───
\section{Certifications}
\textbf{ISO 27001:2022 Lead Implementer} -- Information Security Management Systems (ISMS)

% ─── PUBLICATIONS ───
\section{Research Works}
M Karthikeyan et al., ``\textit{Communicable Disease Prediction Using Machine Learning and Deep Learning Algorithms},'' Inventive Communication and Computational Technologies, pp. 979--992, Springer, Oct 2023.\\
\textit{DOI:} \href{https://doi.org/10.1007/978-981-99-5166-6_66}{10.1007/978-981-99-5166-6\_66}

\end{document}

